%-------------------------
% Resume in Latex
% Author : Larry Chiem 
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{/https://github.com/Chiemychanga}{\Larry Chiem}} & Email : \href{mailto:larrypchiem@gmail.com}{clarry@pdx.edu}\\
  \href{https://github.com/Chiemychanga}{https://github.com/Chiemychanga/} & Mobile : 503-929-2929 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Portland State University}{Portland, OR}
      {Bachelor of Science in Computer Science}{Sept. 2015 - Present}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CDK Global}{Portland, OR}
      {Software Developer Engineer Intern}{June 2017 - Sept 2017}
      \resumeItemListStart
        \resumeItem{DMS Migrations Dashboard}
          {DMS(Data Management Systems) Migrations Dashboard is a dashboard that retrieves a database from JIRA using MongoDB and displays sorted JSON data.}
      \resumeItemListEnd

    \resumeSubheading
      {Portland State University}{Portland, OR}
      {C++ Data Structures Grader}{Sept. 2016 - March 2017}
      \resumeItemListStart
        \resumeItem{Data Structure Programs Grader}
          {Using a grading ruberic from my manager, I troubleshooted student's C++ Data Structureprograms using GDB and valgrind. I graded writing papers and code in this position. I always did my best to give the best feedback to students since I was once in this difficult class.}
      \resumeItemListEnd

    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Research and Teaching Assistant}{Jan 2012 - Dec 2013}
      \resumeItemListStart
        \resumeItem{Research Assistant - Machine Learning}
          {Research on machine learning for portfolio hedging and replication algorithms. Modeling low-risk \& continuous-return strategies. Developed the python library QSTK.}
        \resumeItem{Teaching Assistant - Computational Investing}
          {The online course on Coursera, had more than 100,000 students enrolled. It was featured on the 11 Alive News and the Atlanta Journal Constitution. Involved in creating assignment, exams and conducting recitation sessions. Also taught the on-campus version of the course.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{CDK Chatbot}
      {Integrating a Chatbot on CDK Global's website using Microsoft's Azure Bot Service.}
    \resumeSubItem{Tri-met App}
      {Replicated the Tri-Met app on to a website that always showed a valid expiration time.}
    \resumeSubItem{HYPED! Quackcon Project}
      {Multiplatform responsive web app that created small polls and raffles based off the live game the user is in.}
    \resumeSubItem{Scrabble}
      {A terminal friendly version of Scrabble that allowed a single player vs computer or a 1 vs 1 mode.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: HTML & CSS, Javascript, C++, Java}
%      \hfill
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
